---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## During my time at university I have enjoyed eating sweet treats and the whole process, so I wanted to investigate this little task I get upto in my time.


These are my plots, my first plowhich shows the, the reason I am interested in these plots is because I was curious on the number of sweet treats I would since sometimes I would lose track throughout the days. 


```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTDS720M2fd8gytO6GUbtUSs2YBnvkwJff4e2OEiuSGf0FshxlhtobA-FpoY1oaf_pZKIfDSB5Wo6_N/pub?output=csv")

#https://docs.google.com/spreadsheets/d/e/2PACX-1vTDS720M2fd8gytO6GUbtUSs2YBnvkwJff4e2OEiuSGf0FshxlhtobA-FpoY1oaf_pZKIfDSB5Wo6_N/pub?output=csv




latest_data <- rename(logged_data,
                      time = 2,
                      cost = 3,
                      type = 4,
                      flavour = 5)
#in square brackets create a new data frame, you need it to be 
#a vector by using dollar sign you get a vector, important to know maybe on test
average_cost <- mean(x = latest_data$cost, na.rm = T)


#the minimum cost of a treat for the 3rd index
low_cost <- min(latest_data[3])

#the maximum cost of the cost coloumn
high_cost <- max(latest_data$cost)

#There is a ggplot of sweet to savoury and my plot number 1 
latest_data %>%
  ggplot() +
  geom_bar(aes(y = flavour,
               fill = type,))

#plot number 2 
latest_data %>%
  ggplot() + 
  geom_bar(aes(y = time,
               fill = flavour))

```

The maximum cost for my sweet treat was `r high_cost` and the lowest cost for my sweet treat was `r low_cost`
